### 2019-06-22 ThesisJo/frontmatter.tex
2019-06-22

\begin{document}

@@

\chapter*{Preface}

@@

\newcommand\pubEntry[4]{\item #2, "#1", \textit{#3}, #4}
{\renewcommand{\theenumi}{\textbf{\Roman{enumi}}}
\renewcommand\cleardoublepage{\newpage}
\begin{enumerate}
\pubEntry{%
An Optimized GPU implementation of the MVDR Beamformer for Active Sonar Imaging}%
{J.I. Buskenes, J.P. Åsen, C.-I.C. Nilsen and A. Austeng}%
{IEEE Journal of Oceanic Engineering}%
{Volume 40, Issue 2, April 2015}
%
\pubEntry{%
Implementing Capon Beamformer on a GPU for Real-Time Cardiac Ultrasound Imaging}%
{J.P. Åsen, J.I. Buskenes, C.-I.C. Nilsen, A. Austeng and S. Holm}%
{IEEE Transactions on Ultrasonics, Ferroelectrics, and Frequency Control}%
{Volume 61, Issue 1, January 2015}
%
\pubEntry%
{Low Complexity Adaptive Beamforming}%
{J.I. Buskenes, R.E. Hansen and A. Austeng}%
{IEEE Journal of Oceanic Engineering}%
{Volume 42, Issue 1, January 2017}
%
\pubEntry%
{A Real-Time Synthetic Aperture Sonar Simulator for Automatic Target Recognition: Notation and application}%
{J.I. Buskenes, H. Midelfart}%
{IEEE Journal of Oceanic Engineering}%
{Submitted DD.MM.2018}
\end{enumerate}
%}

>>>>

\begin{document}
\pagestyle{normal}

@@

\chapter*{Preface}
% \cfoot{\thepage}

@@

\newcommand\pubEntry[4]{\item #2\\"#1"\\\textit{#3}\\#4}
{\renewcommand{\theenumi}{\textbf{\Roman{enumi}}}
\renewcommand\cleardoublepage{\newpage}
\begin{enumerate}
\pubEntry{%
An Optimized GPU implementation of the MVDR Beamformer for Active Sonar Imaging}%
{J.I. Buskenes, J.P. Åsen, C.-I.C. Nilsen and A. Austeng}%
{IEEE Journal of Oceanic Engineering}%
{Volume 40, Issue 2, April 2015}
%
\pubEntry{%
Implementing Capon Beamformer on a GPU for Real-Time Cardiac Ultrasound Imaging}%
{J.P. Åsen, J.I. Buskenes, C.-I.C. Nilsen, A. Austeng and S. Holm}%
{IEEE Transactions on Ultrasonics, Ferroelectrics, and Frequency Control}%
{Volume 61, Issue 1, January 2015}
%
\pubEntry%
{Low Complexity Adaptive Beamforming}%
{J.I. Buskenes, R.E. Hansen and A. Austeng}%
{IEEE Journal of Oceanic Engineering}%
{Volume 42, Issue 1, January 2017}
%
\pubEntry%
{Real-Time Synthetic Aperture Sonar Simulation for Automatic Target Recognition: Notation and Application}%
{J.I. Buskenes, H. Midelfart}%
{IEEE Journal of Oceanic Engineering}%
{Submitted DD.MM.2019}
\end{enumerate}
%}
